Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-12-06 paper.tex
Update Figs. 15 & 16 HMNS G(cosA), with new compute-eta data

In Figs.~\ref{fig:nsns_cosA_distrib_I_00deg}
and \ref{fig:nsns_cosA_distrib_I_90deg}, we show the distributions of neutrino
number density over incoming angle
for the observer on the polar axis $\theta=0^\circ$,
and in the equatorial plane $\theta=90^\circ$,
as defined in Eqn.~\ref{eqn:J_per_cosA}.
As in the case of the collapse profile in Sec.~\ref{ssec:test_collapse},
the dominant effect of \emph{scat} on $\tilde{G}(\cos A)$
is to spread the distribution out to larger angles.
\footnote{TODO: also examine spectra or average energies}

\begin{figure}
  \includegraphics[width=\columnwidth]{cosA_distrib-intensity-250km-00deg}
  % Data:   $DIR/Lev1-e30a60b10-{,no}scat-00
  % Script: $DIR/plot-angular_distribution-intensity-compare.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03/000Mo-000.0deg-250km
  \caption{Angular distributions of fluxes for an observer on the rotation axis
    in the hypermassive neutron star configuration
    (presented in Sec.~\ref{ssec:test_disk_comparison}).}
  \label{fig:nsns_cosA_distrib_I_00deg}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{cosA_distrib-intensity-250km-90deg}
  % Data:   $DIR/Lev1-e30a60b10-{,no}scat-00
  % Script: $DIR/plot-angular_distribution-intensity-compare.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03/000Mo-090.0deg-250km
  \caption{Angular distributions of fluxes for an observer in the equatorial
    plane in the hypermassive neutron star configuration
    (presented in Sec.~\ref{ssec:test_disk_comparison}).}
  \label{fig:nsns_cosA_distrib_I_90deg}
\end{figure}

>>>>

In Figs.~\ref{fig:nsns_cosA_distrib_G_00deg}
and \ref{fig:nsns_cosA_distrib_G_90deg}, we show the distributions of neutrino
number density over incoming angle
for the observer on the polar axis $\theta=0^\circ$,
and in the equatorial plane $\theta=90^\circ$,
defined analagously to Eqn.~\ref{eqn:J_per_cosA}.
As in the case of the collapse profile in Sec.~\ref{ssec:test_collapse},
the dominant effect of \emph{scat} on $\tilde{G}(\cos A)$
is to spread the distribution out to larger angles, by generally decreasing
the number of neutrinos coming from the core while increasing the number
of neutrinos coming from the disk.
\footnote{TODO: also examine spectra or average energies}

\begin{figure}
  %\includegraphics[width=\columnwidth]{cosA_distrib-intensity-250km-00deg}
  \resizebox{\columnwidth}{!}{\input{cosA_distrib-G-250km-00deg.tex}}
  % Data:   $DIR/Lev2-e30a150b20-{,no}scat-04
  % Script: $DIR/plot-angular_distribution-number_density-compare.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03/000Mo-000.0deg-250km
  \caption{Distribution of number density $\tilde{G}(\cos A)$ over incoming angle,
    defined analagously to Eqn.~\ref{eqn:J_per_cosA}.
    The integral of this quantity over $d\cos A$ gives the total number density
    measured by this observer on the rotation axis.
    Volume data from the hypermassive neutron star configuration
    (presented in Sec.~\ref{ssec:test_disk_comparison}).}
  \label{fig:nsns_cosA_distrib_G_00deg}
\end{figure}

\begin{figure}
  %\includegraphics[width=\columnwidth]{cosA_distrib-intensity-250km-90deg}
  \resizebox{\columnwidth}{!}{\input{cosA_distrib-G-250km-90deg.tex}}
  % Data:   $DIR/Lev2-e30a150b20-{,no}scat-04
  % Script: $DIR/plot-angular_distribution-number_density-compare.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03/000Mo-090.0deg-250km
  \caption{Distribution of number density $\tilde{G}(\cos A)$ over incoming angle,
    as in Fig.~\ref{fig:nsns_cosA_distrib_G_00deg},
    but with the observer in the equatorial plane.}
  \label{fig:nsns_cosA_distrib_G_90deg}
\end{figure}
